Rapid Cycleway Prioritisation Tool

### 2020-06-10 report.Rmd
Mention dual carriageway limitations
Report updates

```{r, eval=FALSE, echo=FALSE}
citr::tidy_bib_file("~/uaf/allrefs.bib", rmd_file = "report.Rmd", file = "report-refs.bib")
citr::tidy_bib_file("article.Rmd", "~/uaf/allrefs.bib", file = "article-refs.bib")
browseURL("report.pdf")
```

@@

The methodology only selects roads that have the same name for a continuous stretch of at least 500m, as candidates for top routes, meaning that some roads will be excluded from the 'top routes' result due to name changes (although most continuous road sections have consistent names).
To mitigate this limitation, roads that don't meet this criteria can still appear in the 'spare lane' and 'estimated width > 10m' layers.

@@

The coming 'restart' will lead to long lasting changes in transport systems.
Whether these changes include a worsening of air pollution, traffic and road traffic casualty rates, or uptake of active transport is an open question that depends effective and timely interventions.
The Rapid Cycleway Prioritisation Tool provides an evidence base in support of effective and timely interventions that will form part of broader strategies to respond to COVID-19.

@@

>>>>

```{r, eval=FALSE, echo=FALSE}
citr::tidy_bib_file("~/uaf/allrefs.bib", rmd_file = "report.Rmd", file = "report-refs.bib")
citr::tidy_bib_file("article.Rmd", "~/uaf/allrefs.bib", file = "article-refs.bib")
browseURL("report.pdf")
browseURL("report.docx")
```

@@

The methodology only selects roads that have the same name for a continuous stretch of at least 500m, as candidates for top routes, meaning that some roads will be excluded from the 'top routes' result due to name changes (although most continuous road sections have consistent names).
To mitigate this limitation, roads that don't meet this criteria can still appear in the 'spare lane' and 'estimated width > 10m' layers. 
Dual carriageways lengths are currently counted twice, meaning a dual carriageway section of 260 m may be included in the results.

@@

The coming 'restart' will lead to long lasting changes in transport systems.
The changes could include a worsening of air pollution, congestion and road traffic casualty rates.
Alternatively, the restart could involve continued uptake of active transport.
The Rapid Cycleway Prioritisation Tool provides an evidence base in support of effective and timely interventions that can help ensure a healthy, safe restart to the transport system that future proofs it for the demands the 21^st^ Century.

@@

# Credits

Many thanks to Dr Malcolm Morgan ([University of Leeds](http://www.leeds.ac.uk/)) and Martin Lucas-Smith ([CycleStreets.net](https://www.cyclestreets.net/)) for providing substantial input into methodological and web development aspects of the project respectively.

Thanks to Jeremy Clarke, Rabina Nawaz, John Sweetman and Richard Mace from the [Department for Transport](https://www.gov.uk/government/organisations/department-for-transport) for vital input into the tool's design.
Thanks to Kevin McCann from [Sustrans](https://www.sustrans.org.uk/) for guidance that improved the tool from a policy perspective.
Thanks to Roger Geffen and others from [CyclingUK](https://www.cyclinguk.org/) for input into prototype versions of the tool.
Thanks to developers of open source software, especially to [contributors](https://www.r-project.org/contributors.html) to the R language in which most of the data analysis was conducted.
Thanks also to all the contributors to OpenStreetMap who provided open data on which much of the analysis was based, allowing publication of the results as open data under the conditions of the Open Data Commons Open Database License ([ODbL 1.0](https://www.openstreetmap.org/copyright)). Data (c) [OpenStreetMap](https://www.openstreetmap.org) contributors.
